### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: shortened some text in the advanced coalescence section

%\subsection{Advanced coalescence} 
In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}. The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions. They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space. Because coalescence is a quantum-mechanical process, however, the classical definition of phase space does not apply and it is replaced by the Wigner formalism. Therefore, most coalescence models, including \cite{Scheibl:1998tk}, determine the production probability of a nucleon cluster as by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.

The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$. For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains

@@

This ansatz allows one to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wave-function, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations. The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. 
We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. 
The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and to the size of the (hyper-)nucleus. In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.

@@

\begin{equation}
\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
\label{eq:CA_general}
\end{equation}
%
for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised in \cite{Scheibl:1998tk} as
\begin{equation}
\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1} \;\;.
\label{eq:BA_general}
\end{equation}
In particular, for the case of \hethree~with $A=3$ and $J=1/2$, Eq. \ref{eq:BA_general} becomes the Eq. 9 presented in \cite{Blum:2017qnn}:
\begin{equation}
\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
\label{eq:B3}
\end{equation}

\noindent where

 \begin{equation}
\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1} \;\;.
\label{eq:C3}
\end{equation}

>>>>

%\subsection{Advanced coalescence} 
In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp}, in our study we rely on the formalism proposed in~\cite{Scheibl:1998tk}.
%The authors use a density matrix approach to calculate the coalescence probability and the invariant momentum spectra of deuterons and anti-deuterons in heavy-ion collisions. They consider the coalescence of nucleons within a source that is rapidly expanding under collective flow.
The authors use a density matrix approach to calculate the coalescence probability of nucleons within a source that is rapidly expanding under collective flow in heavy-ion collisions.
%The fact that the coalescence probability is anti-proportional to the source volume can already be understood in the classical phase-space picture as due simply to the separation in configuration space. Because coalescence is a quantum-mechanical process, however, the classical definition of phase space does not apply and it is replaced by the Wigner formalism. Therefore, most coalescence models, including \cite{Scheibl:1998tk}, determine the production probability of a nucleon cluster as by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.
As coalescence is a quantum-mechanical process, the classical definition of phase space is replaced by the Wigner formalism. Therefore, the production probability of a nucleon cluster is given by the overlap of the Wigner function of its internal wave-function with the phase-space distributions of the constituent particles.

%The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with a characteristic size parameter $r_{A}$. 
The wave-functions of the objects under study are approximated by the ground-state wave-functions of an isotropic spherical harmonic oscillator as in~\cite{Scheibl:1998tk} with one single characteristic-size parameter, $r_{A}$. 
For the deuteron (A = 2) wave-function $\varphi_{d}(\vec{r}) $, one obtains

@@

In this work, we follow the gaussian ansatz in order to obtain fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and to the size of the (hyper-)nucleus. 
In Tab.~\ref{tab:nucleusradii}, we list the measured rms of the wave-function, $\rmsradius^{meas}$, as well as the $r_{A}$ parameter derived according to these relations. 
We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with more realistic wave-functions, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
%This ansatz allows one to derive in the following a set of analytic formulas which can be used for the calculation of coalescence predictions. In Tab.~\ref{tab:nucleusradii}, we therefore do not list only the rms of the wave-function, but also the size parameter of the harmonic oscillator function, $r_{A}$, derived according to these relations. The approximation of the wave-function with a gaussian form can be further refined with more realistic parameterisations, e.g. the Hulthen parameterisation for the deuteron \cite{Nagle:1996vp} or a $\Lambda$-deuteron parameterisation for the hyper-triton as done for central collisions in~\cite{Zhang:2018euf}. 
%We encourage future more rigorous numerical studies that address the calculation of coalescence probabilities with these more realistic wave-functions. 
%The difference between such calculations and our predictions would also indicate the uncertainty associated with the coalescence model. 
%Nonetheless, in this work, we decide to follow the gaussian ansatz in order to obtain more intuitive and fully analytic solutions that highlight the sensitivity to the size of the source (i.e. the centrality dependence) and to the size of the (hyper-)nucleus. In particular, the gaussian assumption allows one to describe the extension of the wave-function with one single parameter $r_{A}$.

@@

\begin{equation}
\langle C_{A} \rangle = \prod_{i=1,2,3} \left(1 + \frac{r^2}{4R_{i}^2} \right)^{-\frac{1}{2}(A-1)}
\label{eq:CA_general}
\end{equation}
%
for mass number $A$ and the radii $R_{i}$ that describe the volume of the emitting source.
Similarly, the coalescence parameter \bA~for a nucleus with mass number $A$ and spin $J_{A}$ is generalised by Eq. 6.2 in \cite{Scheibl:1998tk}.
%as
%\begin{equation}
%\bA = \frac{2J_{A} +1}{2^{A}}\frac{1}{\sqrt{A}}  \langle C_{A} \rangle \left( \frac{(2\pi)^{3/2}} {m_{T}\prod_{i=1,2,3} R_{i}} \right)^{A-1} \;\;.
%\label{eq:BA_general}
%\end{equation}
In particular, for the case of \hethree~with $A=3$ and $J=1/2$, 
%Eq. \ref{eq:BA_general} 
the latter becomes the Eq. 9 presented in \cite{Blum:2017qnn}.
%\begin{equation}
%\bthree = \frac{(2\pi)^{3}}{4\sqrt{3}} \langle C_{3} \rangle (m_{T}\prod_{i=1,2,3} R_{i})^{-2}
%\label{eq:B3}
%\end{equation}
% 
%\noindent where
%
% \begin{equation}
%\langle C_{3} \rangle \approx \prod_{i=1,2,3} \left(1 + \frac{r_{3}^2}{4R_{i}^2} \right)^{-1} \;\;.
%\label{eq:C3}
%\end{equation}
